---
title: "Assignment_1"
author: "Darius McDaniel"
date: "September 19, 2015"
output: word_document
---
```{r, echo=FALSE, message=F, warning=F}

source("Assignment_1_R.R")
```


1. In what state and in what month was the highest valued cocaine seized ?


To answer this question I first wanted to know some things about the data. First I wanted to make sure the state variables where the same so I could combine the two data sets. Once this was done I used cbind to merge the two. 

Using the dplyr package I used several pipelines to answer the above question. 

I started of by using mutate to find the highest valued cocaine.
Then used filter to find the price that matched the highest price.
I used select to keep only nessesary variables.

```{r , echo = T}
DEA_smh <- DEA%>%
  mutate(highestPrice = max(price))%>%
  filter(highestPrice == price)%>%
  select(state, potency, weight, price, month)
```
Answer:
```{r , echo = F}
print(DEA_smh)

```


2. What state had the one seizure with the highest / maximum potency ?


To answer this question for I used the some of the same methods as in question 1.
But added in arrange decsending by potency and found two states with the same high potency. I then wanted to look at the counts of seizures to see which state had just one seizure and both ME and VA had a count of 1. 

```{r , echo = T}
DEA_pote <- DEA%>%
  mutate(potencyMax = max(potency))%>%
   filter(potencyMax == potency)%>%
  inner_join(count)%>%
  select(state, potencyMax,count)

```
Answer:
```{r , echo = F}
print(DEA_pote)

```

3. Present a table which counts the total number of seizures per state. The table should be arranged in
order of number of seizures from highest to lowest.

Here we add the count by state within summarise then arrange in descending order.
```{r , echo = T}
StateSeiz <- summarise(byState, count = n())%>%
             arrange(desc(count))

```

Answer:
```{r , echo = F}
print(StateSeiz)

```


 
