---
title: "Assignment_1"
author: "Darius McDaniel"
date: "September 19, 2015"
output: word_document
---
```{r, echo=FALSE, message=F, warning=F}

source("Assignment_1_R.R")
```


1. In what state and in what month was the highest valued cocaine seized ?


To answer this question I first wanted to know some things about the data. First I wanted to make sure the state variables where the same so I could combine the two data sets. Once this was done I used cbind to merge the two. 

Using the dplyr package I used several pipelines to answer the above question. 

I started of by using mutate to find the highest valued cocaine.
Then used filter to find the price that matched the highest price.
I used select to keep only nessesary variables.

```{r , echo = T}
DEA_smh <- DEA%>%
  mutate(highestPrice = max(price))%>%
  filter(highestPrice == price)%>%
  select(state, potency, weight, price, month)
```
Answer:
```{r , echo = F}
print(DEA_smh)

```


2. What state had the one seizure with the highest / maximum potency ?



 
